Semantic information inside sentence embeddings

### 2023-05-13 paper/paper.tex
Rewrite probing tasks, part 2

We define \emph{relation vector} as the ....

@@

Again, we report plotted grid search results in
Figure~\ref{fig:cls_gs_no_context_embed_comparison}. Comparing these results to
those in contextualized setting, we see large drop of performance for
\Embed{sbert} embedding --- almost by 50\%. This shows how much the classifiers
relied on the information contained in the embedding of seed sentence. This
drop is not as pronounced for \Embed{sbert\_supervised} embedding, because the
model producing them is optimized with precisely this type of
task.\footnote{For this reason, we avoid comparing \Embed{sbert\_supervised} to
other embeddings from this point onwards.} On the other hand, the BOW
embeddings performed almost as well, suggesting they were not really able to
take advantage of the contextualized setting.

>>>>

We define \emph{relation vector} as the ....
To per
Costra

@@

Again, we report plotted grid search results in
Figure~\ref{fig:cls_gs_no_context_embed_comparison}. Comparing these results to
results for probing transformation vectors, we see large drop of performance for
\Embed{sbert} embedding --- almost by 50\%. This shows how much the classifiers
relied on the information contained in the embedding of seed sentence. This
drop is not as pronounced for \Embed{sbert\_supervised} embedding, because the
model producing them is optimized with precisely this type of
task.\footnote{For this reason, we avoid comparing \Embed{sbert\_supervised} to
other embeddings from this point onwards.} On the other hand, the BOW
embeddings performed almost as well, suggesting they were not really able to
take advantage of the information inside seed embeddings.
